Programmatic Generation of R Markdown Documents with \pkg{listdown}

### 2020-03-08 inst/r-journal/listdown-article.tex
Extra R chunk option checking.

---
title: Programmatic Generation of R Markdown Documents with \pkg{listdown}
author:
  - name: Michael Kane
    affiliation: Yale University
    address:
    - 60 College Street
    - New Haven, CT 06510, USA
    email:  michael.kane@yale.edu
abstract: >
  An abstract of less than 150 words.
preamble: |
  % Any extra LaTeX you need in the preamble
output: rticles::rjournal_article
---

# Background and concepts

R Markdown documents support the construction of reproducible documents by allowing authors to insert R code for data processing, exploration, analysis, table-making, and visualization directly into structured, prose documents. In the context of this document, we will refer to the R code in these documents as _computational components_ since they are generated by computational means (namely the R interpreter). The prose in these documents will be referred to as _narrative components_. They may serve to help a reader understand the background, goal, theme, and results of the paper as well as contextualizing the computational components.

R Markdown [@baumer2014] integrates the process of integrating the computational and narrative components of a document. By itself this is not novel. It was identified as "Literate Programming" by @knuth1984 and software tools, like Sweave [@leisch2002] have supported this functionality for almost two decades. R Markdown's popularity has likely been driven by two factors. The first is the relative ease with which these documents can be constructed. While it is more expressive, \LaTeX is relatively technical and requires an investment in time to become proficient. By contrast R Markdown documents are easier to create and format and, when the document is used to create \LaTeX formatting can be passed through to the underlying .tex file. The second factor driving adoption is likely its support for creating _modifiable_ documents, Microsoft Word in particular. Researchers and analysts, especially those creating applied statistical analyses, often collaborate with domain experts with less technical knowledge. In these cases, the analyst focuses on creating the computational components and narrative components related to results and interpretation. After this initial document is created, the domain expert is free to develop narrative components directly in the document without needing to go through the analyst.

@@

However, this is not to say the programmatic creation of R Markdown documents is unwarranted or not useful. In fact it has at least two appealing characteristics. The first is convenience. <FILL THIS IN - TALK ABOUT REUSE TO MOTIVATE LARGER PIPELINES>. The second is that for fixed analysis pipelines processing uniformly-formatted but domain-distinct data, automated document generation enforces uniformity across those domains being serviced. <FILL THIS IN USE MULTIPLE-HISTOLOGY THERAPY AS AN EXAMPLE>.

The \pkg{listdown} package provides functions to programmatically create R Markdown files from 
named lists. It is intended for data analysis pipelines where the presentation of the results
is separated from their creation. For this use case, a data processing (or analysis) is performed
and the results are provided in a single named list, organized heirarchically. With the list and a \pkg{listdown} object a workflowr [@blischak2019], pdf, word, or html page. List element names denote sections, subsections,
subsubsection, etc. and the list elements contain the data structure to be presented including
graphs and tables. The goal of the package is not to provide a finished, readable document. It is to provide a document with all tables and visualization that will appear (_computational_ components). This serves as a starting point from which a user  can organize outputs, describe a study, discuss results, and provide conclusions (_narrative_ components).

@@

\begin{itemize}
\item{\bf ld\_cc\_dendro() }{- create a dendrogram from a list of computational components}
\item{\bf ld\_chunk\_opts() }{- apply chunk options to a presentation object}
\item{\bf ld\_ioslides\_header() }{- create an ioslides presentation header}
\item{\bf ld\_make\_chunks() }{- write a listdown object to a string}
\item{\bf ld\_workflowr\_header() }{- create a worflowr header}
\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header}
\item{\bf listdown() }{- create a listdown object to create an R Markdown document}
\end{itemize}

@@

# Basic usage and overview

@@

As a first example, we will consider the a list of visualizations from the anscombe data set. The list is composed of four \pkg{ggplot2} [@wickham2016]elements (named Linear, Non Linear, Outlier Vertical, and Outlier Horizontal) each containing a scatter plot from the famous Anscome Quartet - made available in the \pkg{datasets} package [@R]. From the `computational_components` list, we would like to create a document with four sections with names corresponding to the list names, each containing their respective visualizations.

```{r}
# Use ggplot2 to create the visualizations.
library(ggplot2)

@@

# Save the file to disk to be read by the output R Markdown document.
saveRDS(computational_components, "comp-comp.rds")
```

## Creating a document with \pkg{listdown}

Creating a document from the `computational_components` will require two steps. First, we will create a `listdown` object that specifies how the `computational_components` object will be loaded into the document,  which libraries and code needs to be included, the options for the R chunks, and how the list elements will be presented in the output R markdown document.

```{r}
library(listdown)

ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), # The expression to load pres_list in the .Rmd.
               package = "ggplot2")                     # The packges needed to render plots.
```

The `ld` object, along with the computational components in the `comp-comp.rds` file are sufficient to to create the sections, subsections, and R chunks of a document. The only other thing requires to create the document is the header. The listdown package currently supports regular R Markdown, workflowr, and ioslides headers. A complete document can then be written to the console using the code shown below. It could easily be written to a file for rendering using the `writeLines()` function, for example.

```{r}
doc <- c(
  ld_rmarkdown_header("Anscombe's Quartet",
                     author = "Francis Anscombe",
                     date = "1973"),
  ld_make_chunks(ld))

cat(paste(doc, collapse = "\n"))
```

The `listdown()` function provides _document-wide_ R chunk options for displaying computational components. The chunk options are exactly the same as those in the R markdown document and can be used to tailor the default presentation for a variety of needs. The complete set of options can be found in the [R Markdown Reference Guide](https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf). As a concrete example, the code used to create present the plots could be hidden in the output document using the following code.

```{r}
ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
               package = "ggplot2",
               echo = FALSE)

cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
```

## Decorators

The first example is simple in part because the ggplot objects both contain the data we want to display and, at the same time, provide the mechanism for presenting them - rendering them in a graph. However, this is not always the case. The objects being stored in the list of computational components may not translate directly to the presentation in a document. In these cases a function is needed that takes the list component and returns an object to be displayed. For example, suppose that, along with showing graphs from the Anscombe Quartet, we would like to include the data themselves. We could add the data to the `computational_components` list and then create the document with:

```{r}
computational_components$Data <- anscombe
saveRDS(computational_components, "comp-comp.rds")
cat(paste(ld_make_chunks(ld)[32:36], collapse = "\n"))
```

@@

In \pkg{listdown} a function or method that implments the presentation of a computational component is referred to as a _decorator_ since if follows the classic decorator pattern described in @gamma1995. A decorator takes the element that will be presented as an argument and returns an object for presentation in the output directory. A decorator is specified using the `decorator` parameter of the `listdown()` function using a named list where the name corresponds to the type and the element correspond to the function or method that will decorate an object of that type. For example, the `anscombe` data set can be decorated with the `DT::datatable()` function [@xie2020] as:

```{r}
ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
               package = c("ggplot2", "DT"),
               decorator = list(data.frame = datatable))
cat(paste(ld_make_chunks(ld)[33:37], collapse = "\n"))
```

List names in the `decorator` argument provide a key to which a function or method is mapped. The underlying decorator resolution is implemented for a given computational component by going through decorator names sequentially to see if the component inherits from the name using the `inherits()` function. The function or method is selected from the corresponding name which the element first inherits from. This means that when customizing the presentation of objects that inherit from a common class, the more abstract classes should appear at the end of the list. This will ensure that specialized classes will be encountered first in the resolution process.

A separate argument, `default_decorator`, allows the user to specify the default decorator for an object whose type does not appear in the `decorator` list. This allows the user to specify any class name for the decorator and avoids a potential type name collision with a default decorator whose name is determined by convention. By default, this argument is set to `identity` but it can be use to not display a computational component by default if the argument is set to `NULL`.

# Design

A \pkg{listdown} object specifies the location of a list of computational components and options for presenting those components in an R Markdown document. The list is a hierarchical data structure that also provides the structure of the outputted document. A corresponding document has two sections "Iris" and "Sepal.Length". The latter has three subsections "Sepal.Width", "Petal.Length", and "Colored". The "Colored" subsection has two sub-subsections, "Sepal.Width" and "Petal.Length".
The structure can be seen using the `ld_cc_dendro()` function.

```{r}
# Create a more hierarchical list of computational components.
comp_comp2 <- list(
  Iris = iris,
  Sepal.Length = list(
    Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point(),
    Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point(),
    Colored = list(
      Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) + 
        geom_point(),
      Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) + 
        geom_point())))

# Create the dendrogram.
ld_cc_dendro(comp_comp2)
```

Both the `ld_cc_dendro()` and `ld_make_chunks()` functions work by recursively descending the computational components list depth-first. If the list containing and element has a name, it is written to the output as a section, subsection, subsubsection, etc. to a return string. If the visited list element is itself a list, then the same procedure is called on the child list through a recursive call. If the element is not a list, then it is outputted inside an R Markdown chunk in the return string using the appropropriate decorator.

# Advanced usage

@@

## Initialization code

```{r}
saveRDS(comp_comp2, "comp-comp2.rds")
ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
               package = c("ggplot2", "DT", "purrr"),
               decorator = list(ggplot = identity,
                                data.frame = datatable),
               init_expr = {
                 datatable <- partial(datatable,
                                      options = list(dom = 't'))
                 },
               echo = FALSE)

cat(paste(ld_make_chunks(ld)[1:13], collapse = "\n"))
```

## Controlling chunk-level options

@@

```{r}
comp_comp2$Iris <- ld_chunk_opts(comp_comp2$Iris, echo = TRUE)
saveRDS(comp_comp2, "comp-comp2.rds")
cat(paste(ld_make_chunks(ld)[1:19], collapse = "\n"))
```
# Conclusion

@@

>>>>

% !TeX root = RJwrapper.tex
\title{Programmatic Generation of R Markdown Documents with
\pkg{listdown}}
\author{by Michael Kane}

\maketitle

\abstract{%
An abstract of less than 150 words.
}

\hypertarget{background-and-concepts}{%
\section{Background and concepts}\label{background-and-concepts}}

R Markdown documents support the construction of reproducible documents
by allowing authors to insert R code for data processing, exploration,
analysis, table-making, and visualization directly into structured,
prose documents. In the context of this document, we will refer to the R
code in these documents as \emph{computational components} since they
are generated by computational means (namely the R interpreter). The
prose in these documents will be referred to as \emph{narrative
components}. They may serve to help a reader understand the background,
goal, theme, and results of the paper as well as contextualizing the
computational components.

R Markdown \citep{baumer2014} integrates the process of integrating the
computational and narrative components of a document. By itself this is
not novel. It was identified as ``Literate Programming'' by
\citet{knuth1984} and software tools, like Sweave \citep{leisch2002}
have supported this functionality for almost two decades. R Markdown's
popularity has likely been driven by two factors. The first is the
relative ease with which these documents can be constructed. While it is
more expressive, \LaTeX is relatively technical and requires an
investment in time to become proficient. By contrast R Markdown
documents are easier to create and format and, when the document is used
to create \LaTeX formatting can be passed through to the underlying .tex
file. The second factor driving adoption is likely its support for
creating \emph{modifiable} documents, Microsoft Word in particular.
Researchers and analysts, especially those creating applied statistical
analyses, often collaborate with domain experts with less technical
knowledge. In these cases, the analyst focuses on creating the
computational components and narrative components related to results and
interpretation. After this initial document is created, the domain
expert is free to develop narrative components directly in the document
without needing to go through the analyst.

@@

However, this is not to say the programmatic creation of R Markdown
documents is unwarranted or not useful. In fact it has at least two
appealing characteristics. The first is convenience. \textless FILL THIS
IN - TALK ABOUT REUSE TO MOTIVATE LARGER PIPELINES\textgreater. The
second is that for fixed analysis pipelines processing
uniformly-formatted but domain-distinct data, automated document
generation enforces uniformity across those domains being serviced. .

The \pkg{listdown} package provides functions to programmatically create
R Markdown files from named lists. It is intended for data analysis
pipelines where the presentation of the results is separated from their
creation. For this use case, a data processing (or analysis) is
performed and the results are provided in a single named list, organized
heirarchically. With the list and a \pkg{listdown} object a workflowr
\citep{blischak2019}, pdf, word, or html page. List element names denote
sections, subsections, subsubsection, etc. and the list elements contain
the data structure to be presented including graphs and tables. The goal
of the package is not to provide a finished, readable document. It is to
provide a document with all tables and visualization that will appear
(\emph{computational} components). This serves as a starting point from
which a user can organize outputs, describe a study, discuss results,
and provide conclusions (\emph{narrative} components).

@@

\begin{itemize}
\item{\bf ld\_chunk\_opts() }{- apply chunk options to a presentation object}
\item{\bf ld\_ioslides\_header() }{- create an ioslides presentation header}
\item{\bf ld\_make\_chunks() }{- write a listdown object to a string}
\item{\bf ld\_workflowr\_header() }{- create a worflowr header}
\item{\bf ld\_rmarkdown\_header() }{- create an R Markdown header}
\item{\bf listdown() }{- create a listdown object to create an R Markdown document}
\item{\bf to\_data\_tree() }{- create a data.tree object from a list of computational components}
\end{itemize}

@@

\hypertarget{basic-usage-and-overview}{%
\section{Basic usage and overview}\label{basic-usage-and-overview}}

@@

As a first example, we will consider the a list of visualizations from
the anscombe data set. The list is composed of four \pkg{ggplot2}
\citep{wickham2016}elements (named Linear, Non Linear, Outlier Vertical,
and Outlier Horizontal) each containing a scatter plot from the famous
Anscome Quartet - made available in the \pkg{datasets} package
\citep{R}. From the \texttt{computational\_components} list, we would
like to create a document with four sections with names corresponding to
the list names, each containing their respective visualizations.

\begin{Schunk}
\begin{Sinput}
# Use ggplot2 to create the visualizations.
library(ggplot2)

@@

# Save the file to disk to be read by the output R Markdown document.
saveRDS(computational_components, "comp-comp.rds")
\end{Sinput}
\end{Schunk}

\hypertarget{creating-a-document-with}{%
\subsection{\texorpdfstring{Creating a document with
\pkg{listdown}}{Creating a document with }}\label{creating-a-document-with}}

Creating a document from the \texttt{computational\_components} will
require two steps. First, we will create a \texttt{listdown} object that
specifies how the \texttt{computational\_components} object will be
loaded into the document, which libraries and code needs to be included,
the options for the R chunks, and how the list elements will be
presented in the output R markdown document.

\begin{Schunk}
\begin{Sinput}
library(listdown)

ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), # The expression to load pres_list in the .Rmd.
               package = "ggplot2")                     # The packges needed to render plots.
\end{Sinput}
\end{Schunk}

The \texttt{ld} object, along with the computational components in the
\texttt{comp-comp.rds} file are sufficient to to create the sections,
subsections, and R chunks of a document. The only other thing requires
to create the document is the header. The listdown package currently
supports regular R Markdown, workflowr, and ioslides headers. A complete
document can then be written to the console using the code shown below.
It could easily be written to a file for rendering using the
\texttt{writeLines()} function, for example.

\begin{Schunk}
\begin{Sinput}
doc <- c(
  ld_rmarkdown_header("Anscombe's Quartet",
                     author = "Francis Anscombe",
                     date = "1973"),
  ld_make_chunks(ld))

cat(paste(doc, collapse = "\n"))
\end{Sinput}
\begin{Soutput}
#> ---
#> title: "Anscombe's Quartet"
#> author: "Francis Anscombe"
#> date: "1973"
#> output: html_document
#> ---
#> 
#> ```{r}
#> library(ggplot2)
#> 
#> cc_list <- readRDS("comp-comp.rds")
#> ```
#> 
#> # Linear
#> 
#> ```{r}
#> identity(cc_list[[1]])
#> ```
#> 
#> # Non Linear
#> 
#> ```{r}
#> identity(cc_list[[2]])
#> ```
#> 
#> # Outlier Vertical
#> 
#> ```{r}
#> identity(cc_list[[3]])
#> ```
#> 
#> # Outlier Horizontal
#> 
#> ```{r}
#> identity(cc_list[[4]])
#> ```
\end{Soutput}
\end{Schunk}

The \texttt{listdown()} function provides \emph{document-wide} R chunk
options for displaying computational components. The chunk options are
exactly the same as those in the R markdown document and can be used to
tailor the default presentation for a variety of needs. The complete set
of options can be found in the
\href{https://rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf}{R
Markdown Reference Guide}. As a concrete example, the code used to
create present the plots could be hidden in the output document using
the following code.

\begin{Schunk}
\begin{Sinput}
ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
               package = "ggplot2",
               echo = FALSE)

cat(paste(ld_make_chunks(ld)[1:7], collapse = "\n"))
\end{Sinput}
\begin{Soutput}
#> 
#> ```{r echo=FALSE}
#> library(ggplot2)
#> 
#> cc_list <- readRDS("comp-comp.rds")
#> ```
\end{Soutput}
\end{Schunk}

\hypertarget{decorators}{%
\subsection{Decorators}\label{decorators}}

The first example is simple in part because the ggplot objects both
contain the data we want to display and, at the same time, provide the
mechanism for presenting them - rendering them in a graph. However, this
is not always the case. The objects being stored in the list of
computational components may not translate directly to the presentation
in a document. In these cases a function is needed that takes the list
component and returns an object to be displayed. For example, suppose
that, along with showing graphs from the Anscombe Quartet, we would like
to include the data themselves. We could add the data to the
\texttt{computational\_components} list and then create the document
with:

\begin{Schunk}
\begin{Sinput}
computational_components$Data <- anscombe
saveRDS(computational_components, "comp-comp.rds")
cat(paste(ld_make_chunks(ld)[32:36], collapse = "\n"))
\end{Sinput}
\begin{Soutput}
#> # Data
#> 
#> ```{r echo=FALSE}
#> identity(cc_list[[5]])
#> ```
\end{Soutput}
\end{Schunk}

@@

In \pkg{listdown} a function or method that implments the presentation
of a computational component is referred to as a \emph{decorator} since
if follows the classic decorator pattern described in \citet{gamma1995}.
A decorator takes the element that will be presented as an argument and
returns an object for presentation in the output directory. A decorator
is specified using the \texttt{decorator} parameter of the
\texttt{listdown()} function using a named list where the name
corresponds to the type and the element correspond to the function or
method that will decorate an object of that type. For example, the
\texttt{anscombe} data set can be decorated with the
\texttt{DT::datatable()} function \citep{xie2020} as:

\begin{Schunk}
\begin{Sinput}
ld <- listdown(load_cc_expr = readRDS("comp-comp.rds"), 
               package = c("ggplot2", "DT"),
               decorator = list(data.frame = datatable))
cat(paste(ld_make_chunks(ld)[33:37], collapse = "\n"))
\end{Sinput}
\begin{Soutput}
#> # Data
#> 
#> ```{r}
#> datatable(cc_list[[5]])
#> ```
\end{Soutput}
\end{Schunk}

List names in the \texttt{decorator} argument provide a key to which a
function or method is mapped. The underlying decorator resolution is
implemented for a given computational component by going through
decorator names sequentially to see if the component inherits from the
name using the \texttt{inherits()} function. The function or method is
selected from the corresponding name which the element first inherits
from. This means that when customizing the presentation of objects that
inherit from a common class, the more abstract classes should appear at
the end of the list. This will ensure that specialized classes will be
encountered first in the resolution process.

A separate argument, \texttt{default\_decorator}, allows the user to
specify the default decorator for an object whose type does not appear
in the \texttt{decorator} list. This allows the user to specify any
class name for the decorator and avoids a potential type name collision
with a default decorator whose name is determined by convention. By
default, this argument is set to \texttt{identity} but it can be use to
not display a computational component by default if the argument is set
to \texttt{NULL}.

\hypertarget{design}{%
\section{Design}\label{design}}

A \pkg{listdown} object specifies the location of a list of
computational components and options for presenting those components in
an R Markdown document. The list is a hierarchical data structure that
also provides the structure of the outputted document. A corresponding
document has two sections ``Iris'' and ``Sepal.Length''. The latter has
three subsections ``Sepal.Width'', ``Petal.Length'', and ``Colored''.
The ``Colored'' subsection has two sub-subsections, ``Sepal.Width'' and
``Petal.Length''. The structure can be seen using the
\texttt{ld\_cc\_dendro()} function.

\begin{Schunk}
\begin{Sinput}
# Create a more hierarchical list of computational components.
comp_comp2 <- list(
  Iris = iris,
  Sepal.Length = list(
    Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point(),
    Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width)) + geom_point(),
    Colored = list(
      Sepal.Width = ggplot(iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) + 
        geom_point(),
      Petal.Length = ggplot(iris, aes(x = Sepal.Length, y = Petal.Length, color = Species)) + 
        geom_point())))

# Create the dendrogram.
ld_cc_dendro(comp_comp2)
\end{Sinput}
\begin{Soutput}
#> 
#>  comp_comp2
#>   |-- Iris
#>   |  °-- object of type(s):data.frame
#>   °-- Sepal.Length
#>    |-- Sepal.Width
#>    |  °-- object of type(s):gg ggplot
#>    |-- Petal.Length
#>    |  °-- object of type(s):gg ggplot
#>    °-- Colored
#>     |-- Sepal.Width
#>     |  °-- object of type(s):gg ggplot
#>     °-- Petal.Length
#>        °-- object of type(s):gg ggplot 
#> 
\end{Soutput}
\end{Schunk}

Both the \texttt{ld\_cc\_dendro()} and \texttt{ld\_make\_chunks()}
functions work by recursively descending the computational components
list depth-first. If the list containing and element has a name, it is
written to the output as a section, subsection, subsubsection, etc. to a
return string. If the visited list element is itself a list, then the
same procedure is called on the child list through a recursive call. If
the element is not a list, then it is outputted inside an R Markdown
chunk in the return string using the appropropriate decorator.

\hypertarget{advanced-usage}{%
\section{Advanced usage}\label{advanced-usage}}

@@

\hypertarget{initialization-code}{%
\subsection{Initialization code}\label{initialization-code}}

\begin{Schunk}
\begin{Sinput}
saveRDS(comp_comp2, "comp-comp2.rds")
ld <- listdown(load_cc_expr = readRDS("comp-comp2.rds"),
               package = c("ggplot2", "DT", "purrr"),
               decorator = list(ggplot = identity,
                                data.frame = datatable),
               init_expr = {
                 datatable <- partial(datatable,
                                      options = list(dom = 't'))
                 },
               echo = FALSE)

cat(paste(ld_make_chunks(ld)[1:13], collapse = "\n"))
\end{Sinput}
\begin{Soutput}
#> 
#> ```{r echo=FALSE}
#> library(ggplot2)
#> library(DT)
#> library(purrr)
#> 
#> cc_list <- readRDS("comp-comp2.rds")
#> ```
#> 
#> ```{r echo=FALSE}
#> datatable <- partial(datatable, options = list(dom = "t"))
#> ```
\end{Soutput}
\end{Schunk}

\hypertarget{controlling-chunk-level-options}{%
\subsection{Controlling chunk-level
options}\label{controlling-chunk-level-options}}

@@

\begin{Schunk}
\begin{Sinput}
comp_comp2$Iris <- ld_chunk_opts(comp_comp2$Iris, echo = TRUE)
saveRDS(comp_comp2, "comp-comp2.rds")
cat(paste(ld_make_chunks(ld)[1:19], collapse = "\n"))
\end{Sinput}
\begin{Soutput}
#> 
#> ```{r echo=FALSE}
#> library(ggplot2)
#> library(DT)
#> library(purrr)
#> 
#> cc_list <- readRDS("comp-comp2.rds")
#> ```
#> 
#> ```{r echo=FALSE}
#> datatable <- partial(datatable, options = list(dom = "t"))
#> ```
#> 
#> # Iris
#> 
#> ```{r echo = TRUE}
#> datatable(cc_list[[1]])
#> ```
\end{Soutput}
\end{Schunk}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\address{%
Michael Kane\\
Yale University\\
60 College Street\\ New Haven, CT 06510, USA\\
}
\href{mailto:michael.kane@yale.edu}{\nolinkurl{michael.kane@yale.edu}}
